Potential of I/O-Aware Workflows in Climate and Weather

### 2020-02-26 paper.tex
Fin

\item[Abstraction] The user does not have to know the architecture of the target system on which the workflow will run, removing the specialist from the decision-making process.

@@

\small
This project is funded by the European Union's Horizon 2020 research and innovation programme under grant agreement No. 823988.
We thank our collaborators Bryan Lawrence, Glenn Greed, David Matthews, and Hua Huang for their input to this paper.

>>>>

\item[Abstraction] Providing the abstraction that enables a separation of concerns.
Once the IO characteristics for a workflow is defined, the user does not have to know the architecture of the target system on which the workflow will run.
Thus, removing the specialist from the decision-making process of individual workflows.

@@

\small
This project is funded by the European Union's Horizon 2020 research and innovation programme under grant agreement No. 823988.
We thank our collaborators Bryan Lawrence, Glenn Greed, David Matthews, and Hua Huang for their input to this paper, and the NGI initiative for contributions to the vision.
